\documentclass{report}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[brazilian,english]{babel}

\usepackage{changepage}

\usepackage{graphicx}

\usepackage{hyperref}

\usepackage{fontspec}
\setmainfont{xkcd-Regular}

\usepackage{dirtytalk}
\usepackage{epigraph}
\newenvironment{script}{}{\par}
\newcommand{\Epigraph}[2]{\begin{script}\epigraph{\fontfamily{lmss}\selectfont\textit{#1}}{#2}\end{script}}

\usepackage{imakeidx}

\usepackage{afterpage}

\usepackage{amsmath}
\usepackage{esint}

\author{\uppercase Victor S. Santos \\ Aerospace Engineering Undergraduate \\
 Universidade Federal de Minas Gerais}
\title{\uppercase Aerospace Engineering Lecture Notes}

\makeindex

\makeatletter
\let\old@endpart\@endpart
\renewcommand\@endpart[1][]{%
\begin{adjustwidth}{150pt}{-50pt}
\begin{quote}\vfill#1\vfill\end{quote}%
\end{adjustwidth}
\old@endpart}
\makeatother

\begin{document}

\maketitle

\thispagestyle{empty}

\tableofcontents

\frontmatter
% \afterpage{\null\newpage}


\chapter*{Introduction}\addcontentsline{toc}{chapter}{Introduction}\markboth{Introduction}{}

This text is a subjective, personal, non-exhaustive and
not ambitious synthesis of what I've learned, and more important than
anything: were to find stuff about the AE field.

The first part is about the fundamentals and tools required for 
advancing and don't get completely lost.
The second part is an application of those fundamentals 
and tools (a.k.a. engineering).
The third and last part is about crazy stuff.

I made this because I'm a terrible note taker, and I can visualize
a future me wanting some information from the past, and wasting
a ton of time in finding it. I hope that this can be useful to
somebody. But this is for you, future me.

Enjoy.

\mainmatter

\part{\uppercase{Fundamentals}}
[
This is where we just see lectures and more lectures about things that
we think we will never use in our days about Earth. But what if we're
wrong?
]
\include{fundamentals/fundamentals}

\part{\uppercase{Engineering}}
[
When things are starting to get funny, and you 
start to get mad.
]
\include{engineering/engineering}

\part{\uppercase{Advanced Topics}}
[
At this point things transposed the norm barrier
and are getting insane.
But, really, quite useful.
]
\include{advanced/advanced}


\printindex

% \vfill
% \centering{The End.}

\end{document}