
\chapter{Prerequisites}
\Epigraph{``Dammit, I forgot my briefcase.``}{\textit{annoyed dog at the airport}}
First of all, before any theory, equation or anything,
you must know this.
I'm assuming you understand English, have a computer and access to the
internet.

You must like AE, like most things in life, if you
don't truly like what you're doing it's one of the two things: either it doesn't last, or it doesn't end well.

Anyway, everything here doesn't appear from day to night,
it's an everyday
effort (and a endless pursue), so take your time and work on this
with calm and in your own velocity. Remember to breath, drink water,
have fun, be healthy, brush your teeth, and respect your
significant others.

\section{Culture}

As like most human-made things, humanity
has create histories and a sub-culture about aerospace that envelopes
technology, war, beauty, and everything that makes a good novel,
so you could fall in love.

Get on this is good for you, it will make a better professional,
a better academic, and a better person. There is nothing
more sexy then someone passionate about their thing.
But I cannot guide you in this path, this is on you.

\section{How to Find Stuff}

Search Engines are the most powerful tool that
internet can provide us. Get to know how to use them, how to search
and find what you want.

Books historically are a difficult thing to find,
but things got a little different now-days. Here some links
to find books, papers and articles.
But, try a library. Try asking people. Explore.

\begin{description}
    \item{\href{https://gen.lib.rus.ce/}{Library Genesis} -- Every book you can imagine}
    \item{\href{https://sci-hub.tw/}{Sci-Hub} -- Any published paper}
\end{description}{}

\section{Social Skills}

Even that we like flying machines, we're still humans,
and most important this is engineering, this is about and for people.
You must learn how to communicate properly (with your colleagues,
professors, and anyone), being clear, concise and respectful in
the most occasions.

One of the most important skills on a engineer is to be able to
work with other professionals from different areas, the world
is plural, we must have a global view and a shallow wide knowledge
about the world we current live in.

\chapter{Mathematics}

\Epigraph{**sex sounds**}{probably a non-math person}

\section{Calculus}
\subsection{Functions}

There is two kind of functions, the good ones, which you
can work with smoothly, and the bad ones. If you find a bad one
just throw it to the computers.

\subsection{Limits}

A limit is just a mental process were you think about the
nearly impossible in small steps.
But when you finally thing about it, it becomes a thing.

Really, it's just a way to think. You can use limits
to buy groceries if you want.

\subsection{Derivatives}

A fancy way to make a rule of three.

One dimension derivative.
$$\frac{d}{dx}f(x) = \lim_{\Delta x \to 0} \frac{f(x) - f(x+\Delta x)}{\Delta x}$$

Two dimension partial derivative (it goes on).
$$\frac{\partial}{\partial x}f(x, y) = \lim_{\Delta x \to 0} \frac{f(x, y) - f(x+\Delta x,y)}{\Delta x}$$

\subsection{Integrals}

A fancy way to find how much water fills the bucket.
To solve a big one just use a computer or tables.

$$\int f(x) dx = F(x) + C$$
$$\iint f(x,y) dxdy = \int \Big(\int f(x,y) dx\Big) dy$$

\subsection{Series and Sums}
Not cool as Netflix.

\subsection{Theorems}
Behold The Fundamental Theorem of Calculus.
$$F(x) = \int_a^x f(x) dx$$
$$\frac{d}{dx}F(x) = f(x)$$

Stokes Theorem.

\section{Linear Algebra}
\subsection{Vectors}

A pointy dude, but it can point in an N-Dimensional world.
So it's more like a pan-dimensional dude.

$$ u = 
\begin{pmatrix}
u_{1} \\ u_{2} \\ u_{3} \\ u_{4}
\end{pmatrix}
$$

\subsection{Matrices}

Some pointy pan-dimensional dudes stacked side by side.

$$ A = 
\begin{bmatrix}
a_{11} & a_{11} & a_{11} \\
a_{11} & a_{11} & a_{11} \\
a_{11} & a_{11} & a_{11} 
\end{bmatrix} = [a_{ij}]
$$

\subsection{Operators and Properties}

\subsection{Tensors}
Did you think that matrices was very dimensional?
This isn't even my final form, behold the tensors.


\section{Geometry}
\subsection{Analytical Geometry}
\subsection{Non-Euclidean Geometry}

\section{Ordinary Differential Equations}
\section{Partial Differential Equations}

\chapter{Physics}

\section{Mechanics}
\section{Optics}
\section{Electromagnetism}
\section{Thermophysics}

\chapter{Statistics}

\section{Fundamentals}

\chapter{Chemistry}
\Epigraph{Fuck, I hate chemistry.}{me}

\section{Fundamentals}
I really don't know what I can say about chem. Probably that
I just hate it.

\chapter{Computation}

\epigraph{<tec tec tec> ... <Google Search> ... <tec tec tec>}{Some computer guy}

\section{Logic}
\section{Algorithms}
\section{Computer Programming}
